---
title: "Into to Inferential Statistics"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

Lesson 1

Klout score example - Online score (1 -99) credit score for online reputation . Klout score follows bimodal distribution .
Having 40 is good Klout score.

```{r message=FALSE, warning=FALSE}
library(tidyverse)
```

Reading the data
```{r}
klout_data=read_csv('datasets/klout_score.csv')
```

summary statistics
```{r}
summary(klout_data)
```

Below histograms shows distribution is bimodal
```{r}
ggplot(klout_data,aes(x=score))+geom_histogram(bins=40)
```


As per [Central Limit therom](https://en.wikipedia.org/wiki/Central_limit_theorem) , mean of random samples from the distribution is normally distributed.

```{r}
sample_mean=c()

# taking the 35 sample 1000 times taking the average and saving it in the variable.
for (i in 1:1000){
  sample_mean=c(sample_mean,mean(sample(klout_data$score,35,replace=TRUE)))
}

ggplot(data.frame(dist_mean=sample_mean),aes(x=dist_mean))+geom_histogram()
```


As per central limit therom , sample distribution mean is same as population mean
$$\mu=\alpha$$
