---
title: "Into_to_Inferential_Statistics"
output:
  html_document: default
editor_options:
  chunk_output_type: inline
---

Lesson 1

Klout score example - Online score (1 -99) credit score for online reputation . Klout score follows bimodal distribution .
Having 40 is good Klout score.

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggpubr)
```

Reading the data
```{r}
klout_data=read_csv('datasets/klout_score.csv')
```

summary statistics
```{r}
summary(klout_data)
```

Below histograms shows distribution is bimodal
```{r}
ggplot(klout_data,aes(x=score))+geom_histogram(bins=40)
```

lets confirm using qqplot (confirms this is not normal distribution)
```{r}
ggqqplot(klout_data$score)
```


As per [Central Limit therom](https://en.wikipedia.org/wiki/Central_limit_theorem) , mean of random samples from the distribution is normally distributed.

```{r}
sample_mean=c()

# taking the 35 sample 1000 times taking the average and saving it in the variable.
for (i in 1:1000){
  sample_mean=c(sample_mean,mean(sample(klout_data$score,35,replace=TRUE)))
}

ggplot(data.frame(dist_mean=sample_mean),aes(x=dist_mean))+geom_histogram()
```

using qqplot lets confirm if this is normally distributes
```{r}
ggqqplot(sample_mean)
```


while visually inspecting it looks like above plot is normally distributed. Lets also use shapiro test
```{r}
shapiro.test(sample_mean)
```


As per central limit therom , sample distribution mean is same as population mean
$$\mu_{sample distribution} \approx \mu_{population}$$
if the sample size is N , then sample distribution sd is as below
$$\sigma_{sampledistribution}\approx\sigma/\sqrt{N}$$
 Lets validate the above formulas using the Klout dat awe have 
 
 Population standard deviation
```{r}
population_sd=sd(klout_data$score)

cat("population standard deviation is ",population_sd)
```

Sample distribution
```{r}
sample_distribution_sd=sd(sample_mean)

cat("Sample distribution standard deviation is ",sample_distribution_sd)
```

Lets validate the formula 
$$\sigma_{sampledistribution}\approx\sigma/\sqrt{N}$$
Below calculation validates the above formula .
```{r}
population_sd/sqrt(35)
```

```{r}
qqnorm(klout_data$score)
```

